---
title: "p8105_hw5_td2809"
author: "Chris Deng"
date: "2023-11-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

theme_set(theme_minimal() + theme(legend.position = "bottom"))  

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_data =
  read_csv("data/homicide-data.csv", show_col_types = FALSE)
```

The raw data includes `r nrow(homicide_data)` observations and `r length(names(homicide_data))` variables. 

```{r}
# create city_state variable and summarize within cities
homicides_summary = 
  homicide_data  |> 
  mutate(city_state = paste(city, state, sep = ", "))  |> 
  group_by(city_state) |> 
  summarise(
    total_homicides = n(),
    total_unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  ) |> 
  filter(total_unsolved_homicides != 0)

homicides_summary |> 
  head(10) |> 
  knitr::kable()

```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_data =
  homicides_summary  |> 
  filter(city_state == "Baltimore, MD") 

baltimore_unsolved = pull(baltimore_data, total_unsolved_homicides)
baltimore_total = pull(baltimore_data, total_homicides)
baltimore_test = prop.test(baltimore_unsolved, baltimore_total)

broom::tidy(baltimore_test)  |> 
  select(estimate, conf.low, conf.high)
```

Now run `prop.test` for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
city_estimates = homicides_summary  |> 
  group_by(city_state)  |> 
  summarize(
    prop_test = list(prop.test(total_unsolved_homicides, total_homicides))
  )  |>  
  mutate(tidy_test = purrr::map(prop_test, broom::tidy))  |> 
  select(-prop_test)  |> 
  unnest(tidy_test)  |> 
  select(city_state, estimate, conf.low, conf.high) 
```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
ggplot(city_estimates, aes(x = reorder(city_state, estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  coord_flip() +
  labs(x = "City", y = "Proportion of Total Unsolved Homicides")
```

# Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time
```{r}
import_data = function(name, url_path = "data/problem2_data/") {
  read_csv(str_c(url_path, name), show_col_types = FALSE) 
}

files_df = 
  tibble(names = list.files("data/data_p2/")) |> 
  mutate(dat = map(names, ~import_data(.x, "data/data_p2/"))) |>
  unnest(dat) |> 
  mutate(names = str_remove(names, "\\.csv")) |> 
  separate(names, into = c("arm", "id"), sep = "_") |> 
  pivot_longer(
    cols = starts_with("week"),
    names_to = "week",
    values_to = "observation",
    names_prefix = "week_",
    names_transform = list(week = as.numeric)
  )

files_df |> 
  ggplot(aes(x = week, y = observation, group = id, color = id)) +
  geom_line() +
  geom_point() +
  facet_grid(. ~ arm) +
  labs(title = "Observations Over Weeks by Subject")
```
# Problem 3
Set $\mu$ = 0
```{r}
# define parameters
n_simulations = 5000
n = 30
sigma = 5
mu = 0
alpha = 0.05

t_test = function(mu, n, sigma) {
  sample = rnorm(n, mean = mu, sd = sigma)
  test_result = t.test(sample, mu = 0, conf.level = 0.95)
  tidy_result = broom::tidy(test_result) |>
    rename(mu_hat = estimate, p_value = p.value)
  return(tidy_result[c("mu_hat", "p_value")])
}

simulation_results = map_dfr(1:n_simulations, ~t_test(mu, n, sigma))

head(simulation_results)

```
```{r}
mu_list = setNames(1:6, paste("mu =", 1:6))

# Run the simulation for each value of mu
results = map_df(mu_list, function(mu_value) {
  map_dfr(1:n_simulations, ~t_test(mu_value, n, sigma))
}, .id = "mu_label")

# Convert the mu_label to a numeric value for plotting
results = results |>
  mutate(mu = as.numeric(str_extract(mu_label, "\\d+")))

```
```{r}
power_results = results |>
  group_by(mu) |>
  summarise(
    power = mean(p_value < alpha),
    mean_mu_hat = mean(mu_hat),
    mean_mu_rejected = mean(mu_hat[p_value < alpha], na.rm = TRUE)
  ) |>
  ungroup()

# Plotting
power_results |>
  ggplot(aes(x = mu, y = power)) +
  geom_point() +
  geom_line() +
  labs(title = "Power of Different µ", x = "µ", y = "Power")
```
 * The plot shows that the power and effect size are positively correlated.However, after reaching a certain level, the power stabilizes, indicating that additional increases in effect size do not significantly improve the power of the test.
```{r}
power_results |>
  ggplot(aes(x = mu, y = mean_mu_hat)) +
  geom_point(color = "red") +
  geom_line(color = "red") +
  labs(title = "Average Estimate of µ_hat vs. True Value of µ", 
       x = "True Value of µ", 
       y = "Average Estimate of µ_hat")
```
```{r}
power_results |>
  ggplot(aes(x = mu)) +
  geom_point(aes(y = mean_mu_hat, group = 1), color = "blue") +
  geom_line(aes(y = mean_mu_hat, group = 1), color = "blue") +
  geom_point(aes(y = mean_mu_rejected, group = 1), color = "red") +
  geom_line(aes(y = mean_mu_rejected, group = 1), color = "red") +
  labs(
    title = "Average Estimate of µ_hat vs. True Value of µ", 
    x = "True Value of µ", 
    y = "Average Estimate of µ_hat"
  ) +
  scale_color_manual(
    labels = c("All", "Rejected"), 
    values = c("blue", "red")
  ) +
  theme(legend.title = element_blank())

```
 * When the value of $\mu$ is low, the sample average of $\hat\mu$ for tests rejecting the null hypothesis tends to exceed the true value. Conversely, for higher values of $\mu$(such as 4, 5, 6), this sample average of $\hat\mu$ from tests where the null is rejected aligns closely with the true value.
 * It suggests that they are not approximately equal, indicating an overestimation of the true effect when the null is rejected.